\documentclass[letterpaper, 10 pt, conference]{ieeeconf}


\usepackage[colorlinks=true, urlcolor=blue, pdfborder={0 0 0}]{hyperref}
\usepackage{geometry}
\usepackage{overpic}
\graphicspath{{./pictures/pdf/},{./pictures/ps/},{./pictures/png/},{./pictures/jpg/}}
\begin{document}
\author{Aaron T. Becker}
\title{Particle Logic 2.0}
\maketitle

\begin{abstract}
The Robotic Swarm Control Lab (RSCL) exists to
 (1) understand, quantify, and implement the best methods for controlling huge numbers of robots, 
 (2)  implement robotic solutions to medical problems, 
 (3)  train confident, productive, ethical engineers to perform impactful research.

This document explains how to earn lab access and the software suite we use.
\end{abstract}


\begin{itemize}
\item our current memory element is not good enough for a journal submission. It is not conservative.  I'd like to represent state (true or false) by the position of a 2x1 slider.  This slider may require more than 1 CW cycle.

\item a collection of obstacles and 2x1 sliders that work as a one-cycle delay:\\

\begin{centering}
\frame{ reservoir full of 1x1 components} \\
$\downarrow$\\ 
\frame{connecting line that feeds 1x1 components }\\
$\downarrow$\\ 
\frame{   one-cycle-delay      }   \\
\end{centering}
   
OUTPUT:  every other CW cycle a 1x1 block comes out.  Currently we get a new component every CW cycle.  We'd like to get one every other cycle, or concatenate these to get a 1x1 output every n cycles.

\item \emph{Preferential Assembly}
  Add tiny magnets to some of the edges of the sliders so that sliders preferentially assemble if two sliders with mating arrangements hit each other. 
  \begin{itemize}
  	\item how many \emph{species} or \emph{slider varieties} can we construct?
	\item our round sliders rotate, and don't have preferential orientations.  We could weight one side of the sliders.   Could octagonal sliders work in our present system?  Would they rotate?
	\end{itemize} 
\item Develop theory showing that we can use a CW cycle and deliver a polyomino part to a destination, and then with another CW cycle hit this part at an arbitrary location with an additional 1x1 part.  I want to show that we can build arbitrary shaped polyominoes, or prove that certain shapes cannot be constructed. For instance, using our sliders with magnets, can we construct an `o'-shaped arrangement using eight 1x1 sliders?
\item read about \href{http://arxiv.org/abs/1408.3351}{Sandor's aTAM theory} and see if anything practical can be made of it.
 \end{itemize} 
 
 
 \end{document}